### 2021-01-22 research project/sections/Background.tex
""

% $$\pi = \frac{2}{\prod_{k = 0}^{\infty} U_{k}}$$    symbolic
He was able to calculate $\pi$ to a place of 9 decimal points, in 
the year 1593 \cite{Kreminski}, using his method. His method consists 
of finding the area of a polygon of $n$ sides in a circle of constant 
radius. As the value of $n$ is increased, the area of the $n$-gon 
tends toward the area of a circle. The geometric origin of this formula 
can be found using simple right-angle trigonometry, by first finding 
the lengths $OH$ and subsequently $BD$ in Figure 1 (\ref{fig:image1}).

With the radius $R = OB$,

@@

Since the equation for the area of a polygon is defined as $A = \frac{p \cdot a}{2}$, 
where $p$ is the perimeter of the polygon and $a$ is the apothem, in this case $BD \cdot n$ 
and $OH$ respectively.

Let $A_{n}$ equal the area of the polygon with $n$ sides as such: \\
$A_{n} = \frac{OH \cdot BD \cdot n}{2}$ \\
$= \frac{R \cos{\alpha} \cdot 2 R \sin{\alpha} \cdot n}{2} = n R^2 \sin{\alpha} \cos{\alpha}$

@@

So it can be written that, by definition,

@@

Which through the trigonometric identity... // todo

>>>>

% $$\pi = \frac{2}{\prod_{k = 0}^{\infty} U_{k}}$$    symbolic
He was able to calculate $\pi$ to a place of 9 decimal points, in 
the year 1593 \cite{Kreminski}, using his method. His method is reminiscent 
of Archimedes' method, but differs in that it consists of finding 
the area of a polygon of $n$ sides in a circle of constant 
radius, rather than the circumference. As the value of $n$ is increased, the area of the $n$-gon 
tends toward the area of a circle. The geometric origin of this formula 
can be found using simple right-angle trigonometry, by first finding 
the lengths $OH$ and subsequently $BD$ in \ref{fig:image1}.

With the radius of the circle with center $R = OB$,

@@

Since the equation for the area of a polygon is defined as $A = \frac{p \cdot a}{2}$, 
where $p$ is the perimeter of the polygon and $a$ is the apothem, in this case $BD \cdot n$ 
and $OH$ respectively, let $A_{n}$ equal the area of 
the polygon with $n$ sides such that: \\
$A_{n} = \frac{OH \cdot BD \cdot n}{2}$ \\
$= \frac{R \cos{\alpha} \cdot 2 R \sin{\alpha} \cdot n}{2} = n R^2 \sin{\alpha} \cos{\alpha}$

@@

So it can be written that, by definition, the ratio of 
the area of an $n$-gon

@@

Which through the trigonometric identity $\sin{2 \alpha} = 2\sin{\alpha} \cos{\alpha}$ can 
be simplified to:

$\frac{A_{n}}{A_{2n}} = \frac{2\sin{\alpha} \cos{\alpha} }{2\sin{\alpha}}  = \cos{\alpha}$

It can be then written that, through a new variable $P$, \\
$P = \frac{A_{n}}{A_{2n}} \frac{A_{2n}}{A_{4n}} \frac{A_{4n}}{A_{8n}} \dots \frac{A_{(k-2)n}}{A_{kn}} \frac{A_{kn}}{A}$ \\
where $A$ is the area of the circle of radius $R$ 
in \ref{fig:image1}.

So $P = \frac{A_{n}}{A}$, since the values $A_{kn}$ cancel, and 
followingly, it is true that $P = \frac{A_{n}}{A} \Leftrightarrow A = \frac{A_{n}}{P}$. Since 
the area of a circle is defined by $A = \pi R^2$, the value of $R$ being constant in this case,
